---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(dplyr)
library(tidyr)
library(readr)
library(janitor) # for clean_names()
library(stringr)

```

# Get data

```{r}

# # demographics
# data_demographics_raw_messy <- read_csv("../data/raw/data_demographics_raw_messy.csv", skip = 2) |>
#   janitor::clean_names()

data_demographics_raw <- read_csv("../data/raw/data_demographics_raw.csv") |>
  janitor::clean_names()

# self report measure
data_selfreport_raw <- read_csv("../data/raw/data_selfreport_raw.csv") |>
  janitor::clean_names()

# affect attribution procedure
data_amp_raw <- read_csv("../data/raw/data_amp_raw.csv") |>
  janitor::clean_names()

```
# Duplicate unique_ids

```{r}

# do we have duplicate data?
data_demographics_raw |>
  count(subject) |>
  arrange(desc(n))

```

yes - n is different for some subjects

```{r}

dat_unique_id <- data_demographics_raw |>
  rename(unique_id = subject) |>
  count(unique_id) |>
  filter(n == 2) |>
  select(unique_id)
  
```

# Demographics

Clean the demographics data so that summaries of age and gender can be made in the analysis.

```{r}

# wrangle the age data out of the raw
dat_age <- data_demographics_raw |>
  # rename for clarity
  rename(unique_id = subject, item = trialcode) |>
  # select useful columns
  select(unique_id, item, response) |>
  # retain rows that we need
  filter(item == "age") |>
  rename(age = response) |>
  # remove non-numbers or decimals from age
  mutate(age = str_remove_all(age, "[^\\d.]"),  # retains only digits and decimal points
         age = na_if(age, ""),
         age = as.numeric(age)) |>
  select(unique_id, age)
  #select(-item) # alternative: negative selection

# wrangle the gender data out of the raw
dat_gender <- data_demographics_raw |>
  # rename for clarity
  rename(unique_id = subject, item = trialcode) |>
  # select useful columns
  select(unique_id, item, response) |>
  # retain rows that we need
  filter(item == "gender") |>
  rename(gender = response) |>
  # remove non-numbers or decimals from age
  mutate(gender = str_to_lower(gender),
         gender = str_remove_all(gender, "[\\d.]"),
         gender = na_if(gender, ""), 
         gender = case_when(gender == "woman" ~ "female",
                            gender == "yes" ~ NA_character_,
                            gender == "man" ~ "male",
                            gender == "girl" ~ "female",
                            gender == "dude" ~ "male",
                            gender == "non binary" ~ "non-binary",
                            TRUE ~ gender)) |>
  select(unique_id, gender)

```

## Combine

```{r}

# dat_unique_id
# dat_age
# dat_gender

```

# Exclusions / data quality

## AMP

Create an exclusion variable `exclude_amp_performance` based on AMP performance: "exclude" if more than 10% of the test block trials trials are < 100ms, or "include" if not.

Create an exclusion variable `exclude_amp_completeness` based on the AMP having the right number of trials.

```{r}

#data_amp_performance_criteria <- data_amp_raw 

```

# Score measures

## Self-reports

Create a mean score for each participant of the three self-report items.

```{r}

#data_selfreport_trial_level <- data_selfreport_raw 

```

## Affect Misattribution Procedure

Create an overall AMP bias score. Score each trial as having been evaluated as congruent with the prime or not. eg When trialcode == "prime_positive" & evaluative_response == 1, then record as 1, etc. AMP score is the proportion of congruent responses, using the test blocks only.

```{r}

#data_amp_score_congruence <- data_amp_raw 

```

# Combine 

Combine data frames together to create one wide-format data frame where each row represents a participant.

Flag all duplicates for exclusion.

```{r}

# data_processed_before_exclusions 

```

# Define master exclusion variable

```{r}

#data_processed <- data_processed_before_exclusions

```

# Write to disk

```{r}

# # in case this dir doesn't exist, create it
# dir.create("../data/processed/")
# 
# # save data to disk in that dir
# write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Session info

```{r}

sessionInfo()

```


