---
title: "Practicing joins"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(dplyr)
library(readr)

```

# Get data

```{r}

data_unique_id_subset <- read_csv("data_unique_id_subset.csv")
data_age_gender_subset <- read_csv("data_age_gender_subset.csv")
data_amp_summary_subset <- read_csv("data_amp_summary_subset.csv")
data_selfreport_summary_subset <- read_csv("data_selfreport_summary_subset.csv")

nrow(data_unique_id_subset)
nrow(data_age_gender_subset)
nrow(data_amp_summary_subset)
nrow(data_selfreport_summary_subset)

```

# Practicing joins

Using the data frames below and functions from the _join family, write code to do the following joins.  

## Practice 1

create 'data_combined' by joining data_amp_summary_subset and data_age_gender_subset so that unique_ids in either data frame are retained. which join is this? implement it. 

```{r}

# data_combined <- 

```

## Practice 2

create 'data_self_reports_and_their_amp_data' by joining data_selfreport_summary_subset and data_amp_summary_subset so that all participants have self-report data, + AMP data if available. which join is this? implement it. 

```{r}

# data_self_reports_and_their_amp_data <- 

```

## Practice 3

do the opposite: create 'data_amp_data_and_their_self_reports' by joining data_amp_summary_subset and data_selfreport_summary_subset so that all participants have AMP data, + self-report data if available. which join is this? implement it. 

```{r}

# data_amp_data_and_their_self_reports <- 

```

## Practice 4

create data_combined_2 by joining 'data_combined' and data_selfreport_summary_subset only unique_ids already present in data_combined are retained. which join is this? implement it. 

```{r}

# data_combined_2 <- 

```

## Practice 5

create 'data_missing_ids' which should list the unique_ids are missing from data_unique_id_subset but are present in at least one of data_age_gender_subset, data_amp_summary_subset, and data_selfreport_summary_subset. This will require two different joins. Which? Implement them.

```{r}

# data_missing_ids <- 

```



